Commutative Character Sheaves

### 2015-07-25 followup.tex
Push before bed - types

\begin{definition}\label{def:CCS}
A character sheaf on $G$ is \emph{commutative} if there is an isomorphism ${\bar m}^* \gcs{L} \to {\bar m}\op^* \gcs{L}$
such that the following diagram commutes,
  \[
  \begin{tikzcd}[row sep=30]
   \bm^*\gcs{L} \arrow{d} \arrow{r}{\mu} & \LxL \arrow{d}{\vartheta}\\
   \bm\op^*\gcs{L} \arrow{r}{{\bar \theta}^*\mu} &  {\bar \theta}^*(\LxL)
  \end{tikzcd}
  \]
 \end{definition}

 Write $\CCS(G)$ for the full subcategory of $\CS(G)$ consisting of commutative character sheaves.

@@

\subsection{Geometrization of generic data for supercuspidal representations}

As proved in \cite{kim:07a}, many (complex) supercuspidal representations of $p$-adic groups can be built from the generic data of \cite{yu:01a}*{\S 15} and, moreover, the type (in the sense of \cite{bushnell-kutzko:98a}) of the resulting supercuspidal representations can be constructed directly from the generic data. 
%Let us refer to the types arising in this manner as {\it generic types}.
In this section we show that, after fixing an isomorphism $\CC \approx \EE$, every generic type is geometrizable, in the sense that every part of generic type admits a description as a perverse sheaf on a scheme over a finite field, from which the type can be recovered using the trace of Frobenius.

>>>>

\begin{definition}\label{def:CCS}
A character sheaf on $G$ is \emph{commutative} if there is an isomorphism ${\bar m}^* \gcs{L} \to {\bar m}\op^* \gcs{L}$
such that the following diagram commutes,
  \[
  \begin{tikzcd}[row sep=30]
   \bm^*\gcs{L} \arrow{d} \arrow{r}{\mu} & \LxL \arrow{d}{\vartheta}\\
   \bm\op^*\gcs{L} \arrow{r}{{\bar \theta}^*\mu} &  {\bar \theta}^*(\LxL)
  \end{tikzcd}
  \]
 Write $\CCS(G)$ for the full subcategory of $\CS(G)$ consisting of commutative character sheaves.
 \end{definition}

@@

\subsection{Geometrization of generic types for supercuspidal representations}

As proved in \cite{kim:07a}, many (complex) supercuspidal representations of $p$-adic groups can be built from the generic data of \cite{yu:01a}*{\S 15} and, moreover, the type (in the sense of \cite{bushnell-kutzko:98a}) of the resulting supercuspidal representations can be constructed directly from the generic data. 
Let us refer to the types arising in this manner as {\it generic types}.
In this section we show that, after fixing an isomorphism $\CC \approx \EE$, every generic type is geometrizable, in the sense that every part of generic type admits a description as a perverse sheaf on a scheme over a finite field, from which the type can be recovered using the trace of Frobenius.
